---
title: "Welcome to COMP/STAT112"
format: 
  html:
    code-copy: true
---

## Clear Workspace

Always start by clearing the workspace. This ensure objects created in other files are not used here.

```{r}
#| results: 'hide'

rm(list = ls())
```

## List Used Packages

List all the packages that will be used in chunks below.

```{r}
#| results: 'hide'

packages <- c("wordcloud2", "here")
```

## Install Missing Packages

Any missing package will be installed automatically. This ensure smoother execution when run on another machine.

::: callout-important

### Installing Packages on Other People Machine

Be aware that people may not like installing packages into their machine automatically.  This might break some of their previous code.

:::

```{r}
#| results: 'hide'

install.packages(setdiff(packages, rownames(installed.packages())))
```

## Load Packages

```{r results='hide', message=FALSE}
#| results: 'hide'
#| message: FALSE

lapply(packages, require, character.only = TRUE)
```

## Load Dataset

Load some data to visualize.

```{r}
ds <- read.csv(here("data", "msg.csv"))
```

## Visualize Dataset

Visualize data as a wordcloud. The wordcloud will have different colors and alignments each run.

```{r}
wordcloud2(data=ds, shape = "cardioid")
```

## References

-   Céline Van den Rul, How to Generate Word Clouds in R \[[Medium](https://towardsdatascience.com/create-a-word-cloud-with-r-bde3e7422e8a)\]
-   Sean Murphy, Check for installed packages before running `install.packages()` \[[Stack Overflow](https://stackoverflow.com/questions/9341635/check-for-installed-packages-before-running-install-packages)\]
-   Hadley Wickham, The tidyverse style guide \[[Website](https://style.tidyverse.org/index.html)\]
